# First steps {-}

***

If you are using a editor that's not [RStudio](https://www.rstudio.com/), you need
to create a file with the extention .Rmd and open the file is this editor (or 
create the file in the editor and save with this extention, the final result is the
same).

You can do this also in RStudio, but RStudio provide to you another way. In the
first menu option (first option in the up left), you have the options to easily
create a Rmd file (and others types of files and applications^[Take some time to
discovery by yourself this things. Is very simple and intuitive.]).

***

**Important**

> **To use all the R Markdown features you need the R package `rmarkdown`.**

To install the package you only need to run:

```{r, eval=FALSE}
install.packages("rmarkdown")
```

And to load:

```{r, eval=FALSE}
library("rmarkdown")
```

***

## YAML header {-}

In simple documents you don't need to create or use a YAML header, but in general
is a good thing to do.

**YAML**:

*A YAML header explains what type of document to build from your R Markdown file.*

> **A YAML header is a set of key: value pairs at the start of your file. Begin and
    end the header with a line of three dashes (- - -).**

Example:

```{r, eval=FALSE}
___
title: "My first R Markdown document"
author: "Muhammad Lee"
output: htm_document
___
```

Everything that you write inside the YAML is called "metadata".

The output value determines which type of file R will build from your .Rmd file:

* **output: html_document** \(\Rightarrow\) html file (web page)
* **output: pdf_document** \(\Rightarrow\) pdf document
* **output: word_document** \(\Rightarrow\) Microsoft Word .docx
* **output: beamer_document** \(\Rightarrow\) beamer slideshow (pdf)
* **output: ioslides_document** \(\Rightarrow\) ioslides slideshow (html)

> **Here [HTML](http://rmarkdown.rstudio.com/html_document_format.html) and here
    [PDF](http://rmarkdown.rstudio.com/pdf_document_format.html) you can found
    several available YAML options for html and pdf documents.**

## Basic things in Markdown {-}